### 2014-03-14 Draft/background.tex

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.

>>>>

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches have demonstrated to achieve 97\%~\cite{KleinNIPS03} accuracy in classifying POS tags for well written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can achieve around 90\%~\cite{KleinNIPS03} accuracy in classifying phrases and clauses over well written news articles.

### 2014-03-14 Draft/related.tex

Our proposed approach touches a few research areas such as software verification,
NLP on software engineering artifacts, and document augmentation.
We next discuss the relevant work pertinent to our proposed approach in these areas.

\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
Design by contracts has been an influential concept in the area of software engineering in the past decade.
A significant amount of work has been done in automated inference of code contracts.
There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.
Furthermore, there are existing approaches that infer code-contract-like specifications
(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.

>>>>

Our proposed approach touches a few research areas such as software verification,
NLP in software engineering, and document augmentation.
We next discuss the relevant work pertinent to our proposed approach in these areas.

%\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
Formal specifications such as code contracts have been an active area of research. Notably, code contracts that are the heart of design by contract approach have been very influential in the area of software engineering.
A significant amount of work has been done in automated inference of code contracts.
Existing approaches statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.
Furthermore, there are existing approaches that infer code-contract-like specifications
(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.
